Evaluation of classical correlation functions from 2/3D images on CPU and GPU architectures: introducing CorrelationFunctions.jl

### 2023-09-05 paper-correlations.tex
almost done paper

\begin{abstract}
Correlation functions are becoming one of the major tools for quantification of structural information that is usually represented as material's 2D or 3D image.
In this paper we introduce \code{CorrelationFunctions.jl} open-source package developed in Julia and capable of computing all classical
correlation functions based on imaging input data. Images include both binary and multi-phase representations.
Our code is capable of evaluating two-point probability $S_2$, cluster $C_2$, lineal-path $L_2$, surface-surface $F_ss$,
surface-void $F_sv$, pore-size $P$ and chord-length $p$ functions on both CPU and GPU architectures.
There possible, we presented two types of computations: full correlation map (correlations of each point with other pints on the image, that also allows obtaining ensemble averaged CF) and directional correlation functions (currently in major orthogonal and diagonal directions). 
Such an implementation allowed for the first time to assemble a completely free solution to evaluate correlation functions under any operating system with well documented API. Our package includes automatic tests against analytical solutions that are described in this paper. We measured wall times for all CPU and GPU implementations and as a rule of thumb full correlation maps on GPU are faster than directional scans using CPU due to the usage of fast Fourier transform. However, full maps require more RAM and, thus, are limited to available GPU RAM resources. On the other hand, directional CFs are memory efficient and can be evaluated for huge datasets - this way they are the first candidates for
structural data compression of feature extraction. The package itself is available through Julia package ecosystem and on GitHub 
(https://github.com/fatimp/CorrelationFunctions.jl), the latter source also contains documentation and additional helpful resources such as tutorials.
We believe that a single powerful computational tool such as \code{CorrelationFunctions.jl} will significantly facilitate the usage of correlation
functions in numerous areas of structural description and research, as well as in machine learning applications. We also present some example as applied to
ceramic, soil composite and oil-bearing rock samples based on their 3D X-ray tomography and 2D scanning electron microscope images. Finally, we conclude our paper with
discussion of possible ways to further improve presented computational framework.
\end{abstract}

>>>>

\begin{abstract}
Correlation functions are becoming one of the major tools for quantification of structural information that is usually represented as material's 2D or 3D image.
In this paper we introduce \code{CorrelationFunctions.jl} open-source package developed in Julia and capable of computing all classical
correlation functions based on imaging input data. Images include both binary and multi-phase representations.
Our code is capable of evaluating two-point probability $S_2$, cluster $C_2$, lineal-path $L_2$, surface-surface $F_{ss}$,
surface-void $F_{sv}$, pore-size $P$ and chord-length $p$ functions on both CPU and GPU architectures.
There possible, we presented two types of computations: full correlation map (correlations of each point with other pints on the image, that also allows obtaining ensemble averaged CF) and directional correlation functions (currently in major orthogonal and diagonal directions). 
Such an implementation allowed for the first time to assemble a completely free solution to evaluate correlation functions under any operating system with well documented application programming interface (API). Our package includes automatic tests against analytical solutions that are described in the paper. We measured wall times for all CPU and GPU implementations and as a rule of thumb full correlation maps on GPU are faster than directional scans using CPU due to the usage of fast Fourier transform. However, full maps require more RAM and, thus, are limited to available GPU RAM resources. On the other hand, directional CFs are memory efficient and can be evaluated for huge datasets - this way they are the first candidates for
structural data compression of feature extraction. The package itself is available through Julia package ecosystem and on GitHub 
(https://github.com/fatimp/CorrelationFunctions.jl), the latter source also contains documentation and additional helpful resources such as tutorials.
We believe that a single powerful computational tool such as \code{CorrelationFunctions.jl} will significantly facilitate the usage of correlation
functions in numerous areas of structural description and research, as well as in machine learning applications. We also present some example as applied to
ceramic, soil composite and oil-bearing rock samples based on their 3D X-ray tomography and 2D scanning electron microscope images. Finally, we conclude our paper with
discussion of possible ways to further improve presented computational framework.
\end{abstract}
